---
title: "VisualSARSDiff"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{VisualSARSDiff}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error=TRUE
)

```

```{r setup}
library(VisualSARSDiff)
```
## Introduction

Protein-Protein interactions are one of the most important sub-cellular functions in nature. Because of them, many life-saving vaccines and other important breakthroughs in the medical field have become possible. With lots of databases having much information on them, it is important to ensure that all protein-protein interactions can be easily seen and visualized when starting research.


## About this Package

VisualSARSDiff is a package that allows you to model and compare Protein-Protein Interactions. Proteins Interactions can be gotten from the intAct database, as long as you have one or more UNIPROT Protein IDs. With the IDs, you can get raw Protein-Protein Interaction data that can be used in independent studies, a Protein-Protein interaction graph, as well as comparing 2 different proteins and seeing if they have any overlap with regard to proteins they interact with in a easy, graphical way. What started off as an idea with only comparing different corona virus sequences, such as MERS and SARS-CoV-2 expanded to something so much more. While still retaining default functionality to compare your proteinID  to the SARS-CoV-2 Spike protein, lots of custom functionality has been added so that you are able to easily and accurately compare different protein interactions. 


## Available Functions

VisualSARSDiff has 3 main functions:

* `createProteinInteractionGraph()`
    * Taking in a proteinID, this returns a beautiful and easy to read Protein Interaction graph oulining proteins that proteinID                interacts with.
* `getProteinInteractionData()`
    * Gives you raw interaction data straight from the intAct database. Contains original databases, and combinations of matched     ProteinIds.   
* `compareProteinInteractions()`
    * Given 2 proteinIDs, this returns a Venn Diagram that lets the reader if there are any overlapping proteins that both proteinIds end up interacting with. 
    

## Examples 

### Creating a Protein Interaction Graph

```{r}
library(VisualSARSDiff)
#Create a Protein Interaction Graph of the spike protein of SARS-CoV-2
createProteinInteractionGraph("P0DTC2")

```

### Getting raw Protein Interaction Data

```{r}
library(VisualSARSDiff)
#Create raw data straight from the intAct database - intended for independent research use
getProteinInteractionData("P0DTC2")

```

### Compare and see if 2 different proteins interact with similar proteins

```{r}
library(VisualSARSDiff)
#Seeing if the SARS-CoV-2 Spike protein and a Angiotensin-converting enzyme of a little brown bat have interactons
compareProteinInteractions("P0DTC2","G1PXH7")

#Note that these 2 are the same - as if you do not include a second paramter, it defaults to the spike protein mentioned
compareProteinInteractions("P0DTC2","G1PXH7")

```
